Feature importance analysis

### 2020-04-20 analysis/feature-importance.Rmd
wflow_publish(knitr_in("analysis/feature-importance.Rmd"), view = FALSE,     verbose = TRUE)

```{r fi-hr-ale, dev = c("png", "pdf")}
fi_ale_hr_buffer2$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) & scale_y_continuous(
  n.breaks = 2
) &
  labs(y = "ALE") &
  theme_pubr(base_size = 14) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.title.y = element_text(size = 8),
    axis.text.y = element_text(size = 9)
  )
```

@@

```{r}
fi_ale_hr_buffer2_gs20$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) & scale_y_continuous(
  n.breaks = 2
) &
  labs(y = "ALE") &
  theme_pubr(base_size = 14) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.title.y = element_text(size = 8),
    axis.text.y = element_text(size = 9)
  )
```

@@

```{r fi-vi-ale, dev = c("png", "pdf")}
fi_ale_vi_buffer2$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) & scale_y_continuous(
  n.breaks = 2
) &
  labs(y = "ALE") &
  theme_pubr(base_size = 14) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.title.y = element_text(size = 8),
    axis.text.y = element_text(size = 9)
  )
```

@@

```{r}
fi_ale_vi_buffer2_gs20$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) & scale_y_continuous(
  n.breaks = 2
) &
  labs(y = "ALE") &
  theme_pubr(base_size = 14) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.title.y = element_text(size = 8),
    axis.text.y = element_text(size = 9)
  )
```

>>>>

```{r fi-hr-ale, dev = c("png", "pdf")}
ale_p1 = fi_ale_hr_buffer2$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) & scale_y_continuous(
  n.breaks = 2
) &
  labs(y = "ALE") &
  theme_pubr(base_size = 14) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.title.y = element_text(size = 8),
    axis.text.y = element_text(size = 9)
  )

# Custom y axis breaks for subplots
ale_p1[[2]] = ale_p1[[2]] + scale_y_continuous(
  n.breaks = 3
)

ale_p1[[3]] = ale_p1[[3]] + scale_y_continuous(
  n.breaks = 4
)

ale_p1[[7]] = ale_p1[[7]] + scale_y_continuous(
  n.breaks = 4
)

ale_p1[[8]] = ale_p1[[8]] + scale_y_continuous(
  n.breaks = 4
)

ale_p1[[9]] = ale_p1[[9]] + scale_y_continuous(
  n.breaks = 4
)

ale_p1[[10]] = ale_p1[[10]] + scale_y_continuous(
  n.breaks = 4
)

```

@@

```{r}
ale_p2 = fi_ale_hr_buffer2_gs20$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) & scale_y_continuous(
  n.breaks = 2
) &
  labs(y = "ALE") &
  theme_pubr(base_size = 14) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.title.y = element_text(size = 8),
    axis.text.y = element_text(size = 9)
  )

# Custom y axis breaks for subplots
ale_p2[[1]] = ale_p2[[1]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[2]] = ale_p2[[2]] + scale_y_continuous(
  n.breaks = 5
)
ale_p2[[3]] = ale_p2[[3]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[4]] = ale_p2[[4]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[6]] = ale_p2[[6]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[7]] = ale_p2[[7]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[10]] = ale_p2[[10]] + scale_y_continuous(
  n.breaks = 3
)
```

@@

```{r fi-vi-ale, dev = c("png", "pdf")}
ale_p3 = fi_ale_vi_buffer2$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) & scale_y_continuous(
  n.breaks = 2
) &
  labs(y = "ALE") &
  theme_pubr(base_size = 14) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.title.y = element_text(size = 8),
    axis.text.y = element_text(size = 9)
  )

# Custom y axis breaks for subplots
ale_p3[[1]] = ale_p3[[1]] + scale_y_continuous(
  n.breaks = 4
)
ale_p3[[2]] = ale_p3[[2]] + scale_y_continuous(
  n.breaks = 4
)
ale_p3[[3]] = ale_p3[[3]] + scale_y_continuous(
  n.breaks = 4
)
ale_p3[[4]] = ale_p3[[4]] + scale_y_continuous(
  n.breaks = 4
)
```

@@

```{r}
ale_p4 = fi_ale_vi_buffer2_gs20$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) & scale_y_continuous(
  n.breaks = 2
) &
  labs(y = "ALE") &
  theme_pubr(base_size = 14) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.title.y = element_text(size = 8),
    axis.text.y = element_text(size = 9)
  )

# Custom y axis breaks for subplots
ale_p4[[2]] = ale_p3[[2]] + scale_y_continuous(
  n.breaks = 4
)
ale_p4[[3]] = ale_p3[[3]] + scale_y_continuous(
  n.breaks = 4
)
ale_p4[[4]] = ale_p3[[4]] + scale_y_continuous(
  n.breaks = 4
)
```
